My title

### 2024-11-01 paper/paper.qmd
model updated
model updated

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false
#### Workspace setup ####
library(tidyverse)
library(knitr)
library(dplyr)
library(arrow)
set.seed(912)
#### Read data ####
train_DeeSantis <- read_parquet(here::here("data/02-analysis_data/01-training/train_DeSantis.parquet"))
train_Trump <- read_parquet(here::here("data/02-analysis_data/01-training/train_Trump.parquet"))
train_Harris <- read_parquet(here::here("data/02-analysis_data/01-training/train_Harris.parquet"))
Trump_model <- readRDS(here::here("models/Trump_model.rds"))

```

# Introduction

# Data {#sec-data}

## Overview

## Raw data

## Cleaned data

## Measurement

## Similar dataset

# Model

## Model set-up
```{r}
names(train_Trump)
```

```{r, fig.width=10, fig.height=10}
data2 = train_Trump %>% select("numeric_grade","pollscore","transparency_score","sample_size","duration")
pairs( data2 , main = "Predictor vs predictor")
```

```{r}
par(mfrow=c(2,2))
plot(Trump_model,1)
plot(Trump_model,2)
plot(Trump_model,3)
plot(Trump_model,4)
```

```{r}
column_names <- c("transparency_score", "ranked_choice_reallocated","methodology","hypothetical", "population")
variables_string <- paste(column_names, collapse = " + ")
formula_string <- paste("score ~", variables_string)
formula <- as.formula(formula_string)
m2 <- lm(formula, data = train_Trump)
summary(m2)
```

## Predictor variables
